Practical Parametricity for GADTs

### 2020-10-01 20-gadts/inf-rules.tex
repair small error
repaired small errors

We can also prove by simultaneous induction that our interpretations
of types interact well with demotion of functorial variables. Indeed,
we have that, if $\rho, \rho' : \oCPOenv$, \,$f : \rho \to \rho'$,
\,$\rho \phi = \rho \psi = \rho' \phi = \rho' \psi$, \, $f \phi = f
\psi = \id_{\rho \phi}$,\, $\Gamma; \Phi, \phi^k \vdash F$,\,
$\Gamma;\Phi,\ol{\alpha} \vdash G$,\, $\Gamma;\Phi,\alpha_1...\alpha_k
\vdash H$, and $\ol{\Gamma;\Phi \vdash K}$, then
{\color{red} WE NEED TO CHECK LAN CASES HERE!}
\begin{gather}
\label{thm:demotion-objects}
\oCPOsem{\Gamma; \Phi, \phi \vdash F} \rho = \oCPOsem{\Gamma, \psi; \Phi
  \vdash F[\phi :== \psi] } \rho\\
\label{thm:demotion-morphisms}
\oCPOsem{\Gamma; \Phi, \phi \vdash F} f = \oCPOsem{\Gamma, \psi; \Phi
  \vdash F[\phi :== \psi]} f\\
\label{eq:subs-var}
\oCPOsem{\Gamma;\Phi \vdash G[\ol{\alpha := K}]}\rho =
\oCPOsem{\Gamma;\Phi,\ol{\alpha} \vdash G}\rho[\ol{\alpha := 
\oCPOsem{\Gamma;\Phi \vdash K}\rho}]\\
\label{eq:subs-var-morph}
\oCPOsem{\Gamma;\Phi \vdash G[\ol{\alpha := K}]}f =
\oCPOsem{\Gamma;\Phi,\ol{\alpha} \vdash G}f[\ol{\alpha :=
\oCPOsem{\Gamma;\Phi \vdash K}f}]\\
\label{eq:subs-const}
\oCPOsem{\Gamma; \Phi \vdash F[\phi := H]}\rho
= \oCPOsem{\Gamma; \Phi, \phi \vdash F}\rho
[\phi := \lambda \ol{A}.\, \oCPOsem{\Gamma;\Phi,\overline{\alpha}\vdash
    H}\rho[\overline{\alpha := A}]] \\ 
\label{eq:subs-const-morph}
\oCPOsem{\Gamma; \Phi \vdash F[\phi := H]}f
= \oCPOsem{\Gamma; \Phi, \phi \vdash F}f
[\phi := \lambda \ol{A}.\,\oCPOsem{\Gamma;\Phi,\overline{\alpha}\vdash
    H}f[\overline{\alpha := \id_{\ol{A}}}]] 
\end{gather}
Identities analogous to (\ref{thm:demotion-objects}) through
(\ref{eq:subs-const-morph}) hold for relational interpretations as
well.

@@

\new{In the fourth-to-last clause of Definition~\ref{def:set-interp},
  $\iota_{Z, f}$ is the injection into
\[\colim{\ol{Z : \Set_0},\, \ol{f : \oCPOsem{\Gamma; \ol\alpha \vdash K}
    \rho[\ol{\alpha := Z}] \to \oCPOsem{\Gamma; \Phi \vdash
      K[\ol{\alpha := A}]} \rho}}{\,\oCPOsem{\Gamma; \Phi, \ol\alpha
    \vdash F} \rho[\ol{\alpha := Z}]}\]

}

>>>>

We can also prove by simultaneous induction that our interpretations
of types interact well with demotion of functorial variables. Indeed,
we have that, if $\rho, \rho' : \oCPOenv$, \,$f : \rho \to \rho'$,
\,$\rho \phi = \rho \psi = \rho' \phi = \rho' \psi$, \, $f \phi = f
\psi = \id_{\rho \phi}$,\, $\Gamma; \Phi, \phi^k \vdash F$,\,
$\Gamma;\Phi,\ol{\alpha} \vdash G$,\, $\Gamma;\Phi,\alpha_1...\alpha_k
\vdash H$, and $\ol{\Gamma;\Phi \vdash K}$, then
\begin{gather}
\label{thm:demotion-objects}
\oCPOsem{\Gamma; \Phi, \phi \vdash F} \rho = \oCPOsem{\Gamma, \psi; \Phi
  \vdash F[\phi :== \psi] } \rho\\
\label{thm:demotion-morphisms}
\oCPOsem{\Gamma; \Phi, \phi \vdash F} f = \oCPOsem{\Gamma, \psi; \Phi
  \vdash F[\phi :== \psi]} f\\
\label{eq:subs-var}
\oCPOsem{\Gamma;\Phi \vdash G[\ol{\alpha := K}]}\rho =
\oCPOsem{\Gamma;\Phi,\ol{\alpha} \vdash G}\rho[\ol{\alpha := 
\oCPOsem{\Gamma;\Phi \vdash K}\rho}]\\
\label{eq:subs-var-morph}
\oCPOsem{\Gamma;\Phi \vdash G[\ol{\alpha := K}]}f =
\oCPOsem{\Gamma;\Phi,\ol{\alpha} \vdash G}f[\ol{\alpha :=
\oCPOsem{\Gamma;\Phi \vdash K}f}]\\
\label{eq:subs-const}
\oCPOsem{\Gamma; \Phi \vdash F[\phi := H]}\rho
= \oCPOsem{\Gamma; \Phi, \phi \vdash F}\rho
[\phi := \lambda \ol{A}.\, \oCPOsem{\Gamma;\Phi,\overline{\alpha}\vdash
    H}\rho[\overline{\alpha := A}]] \\ 
\label{eq:subs-const-morph}
\oCPOsem{\Gamma; \Phi \vdash F[\phi := H]}f
= \oCPOsem{\Gamma; \Phi, \phi \vdash F}f
[\phi := \lambda \ol{A}.\,\oCPOsem{\Gamma;\Phi,\overline{\alpha}\vdash
    H}f[\overline{\alpha := \id_{\ol{A}}}]] 
\end{gather}
Identities analogous to (\ref{thm:demotion-objects}) through
(\ref{eq:subs-const-morph}) hold for relational interpretations as
well.

@@

In the fourth-to-last clause of Definition~\ref{def:set-interp},
  $\iota_{Z, f}$ is the injection into
\[\colim{\ol{Z : \Set_0},\, \ol{f : \oCPOsem{\Gamma; \ol\alpha \vdash K}
    \rho[\ol{\alpha := Z}] \to \oCPOsem{\Gamma; \Phi \vdash
      K[\ol{\alpha := A}]} \rho}}{\,\oCPOsem{\Gamma; \Phi, \ol\alpha
    \vdash F} \rho[\ol{\alpha := Z}]}\]
